Methods

### 2022-07-05 article/methods.Rmd
checked woodC22db

@@

<!-- Correlated variables were grouped into multi-way ANOVAs---namely biomass, wood density, and diameter in one group; and height, stem density, and wood density in a different group.  -->
Non-linear regressions were run using the function *poly()* in the base R package *stats* `r packageVersion("stats")`, 
which was only ultimately recorded for stem density and richness variables, based on significance and explained variance over linear models. 
All trees censused were included in each analysis including unidentified taxa that represented a single group in taxa-specific analyses.
Community analysis and ordination was done as a PERMANOVA with the *adonis()* function from the *vegan* `r packageVersion("vegan")` R package *[@dixon03]*.
Data and code were organized with R packages *here* *[@here]*, *bookdown* *[@bookdown2022]*, and *grateful* *[@grateful]*, and are available at [nmedina17.github.com/osa](nmedina17.github.com/osa).

>>>>

**Trait matching with *[@doraisami22]* **

@@

<!-- Correlated variables were grouped into multi-way ANOVAs---namely biomass, wood density, and diameter in one group; and height, stem density, and wood density in a different group.  -->
Non-linear regressions were run using the function *poly()* in the base R package *stats* `r packageVersion("stats")`, 
which was only ultimately recorded for stem density and richness variables, based on significance and explained variance over linear models. 
All trees censused were included in each analysis including unidentified taxa that represented a single group in taxa-specific analyses.
Community analysis and ordination was done as a PERMANOVA with the *adonis()* function from the *vegan* `r packageVersion("vegan")` R package *[@dixon03]*.
Data and code were organized with R packages *here* *[@here]*, *bookdown* *[@bookdown2022]*, and *grateful* *[@grateful]*, and are stored at [nmedina17.github.com/osa](nmedina17.github.com/osa).
